---
title: "scRNA-seq"
author: "Tim Lai"
date: "4/21/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load Libraries

```{r, message=FALSE, warning=FALSE}
library(dplyr)
library(Seurat)
library(patchwork)
library(ggplot2)
library(sctransform)
library(clustree)
```

## Input Pipeline
Read in the file and create a seurat object.

```{r}
setwd("C:/users/Tim/Documents")
raw_counts <- read.table("GSE126074_CellLineMixture_SNAREseq_cDNA_counts.tsv")

seurat_obj <- CreateSeuratObject(counts = raw_counts)
seurat_obj
```

## Preprocessing and Normalizations

### Filtering
We detect genes with relatively high mitochondrial content and extreme RNA features for filtering.
```{r}
seurat_obj[["percent.mt"]] <- PercentageFeatureSet(seurat_obj, pattern = "^MT-")
```

Violin plot
```{r, echo=FALSE}
VlnPlot(seurat_obj, features = c("nFeature_RNA", "nCount_RNA", "percent.mt"), ncol = 3)
```

```{r, echo=FALSE}
FeatureScatter(seurat_obj, feature1 = "nFeature_RNA", feature2 = "percent.mt")
```


Based on these plots, we cut off mitochondrial content at 15%. In addition, we target genes with between 200 and 1700 RNA features.
```{r}
seurat_obj <- subset(seurat_obj, subset = nFeature_RNA > 200 & nFeature_RNA < 1700 & percent.mt < 15 & percent.mt > 2)
```

### Normalization
```{r, warning=FALSE}
seurat_obj <- SCTransform(seurat_obj, vars.to.regress = "percent.mt", verbose = FALSE)
```
## Clustering
### PCA
```{r}
seurat_obj <- RunPCA(seurat_obj, npcs = 30, verbose = FALSE)

```


```{r, echo=FALSE}
ElbowPlot(seurat_obj)
```

From the plot, we determine we should use the first ten principal components.

## Make a bunch of clusters

```{r, message=FALSE}
seurat_obj <- FindNeighbors(seurat_obj, dims = 1:10)
seurat_obj <- FindClusters(seurat_obj, resolution = seq(0.2, 2.0, 0.2))
```

## Evaluate clusters
From the cluster tree, we see that tree starts splitting at 0.8. Therefore, we opt for a resolution of 0.2.
```{r, echo=FALSE}
clustree(seurat_obj, prefix = "SCT_snn_res.")
```

Set resolution to 0.2
```{r}
Idents(seurat_obj) <- "SCT_snn_res.0.2"
```

## UMAP
```{r}
seurat_obj <- RunUMAP(seurat_obj, dims=1:10)
```

```{r}
DimPlot(seurat_obj, group.by="ident", reduction = "umap")
```